%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Integrated Communications/Navigation/Mission systems Technician} % Job title
    {United States Air Force} % Organization
    {Clovis, NM} % Location
    {2015 - 2017} % Date(s)
   {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item{Analyze malfunctions, inspect, remove, maintain, and install integrated avionics systems.}
         \item{Provide time sensitive maintenance during preflight operations to facilitate on-time takeoff.}
         \item{Train incoming maintainers on various aircraft systems.}
         \item{Perform and supervise avionics maintenance and general aircraft servicing and handling.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Weapons Systems Controller} % Job title
    {United States Air Force} % Organization
    {Clovis, NM} % Location
    {2015 - 2017} % Date(s)
   {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item{Track and report maintenance status and flight operations of fleet.}
         \item{Facilitate flightline maintenance operations on and off base.}
         \item{Deployed to Afghanistan in 2016}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Systems Engineer} % Job title
    {OSU Open Source Laboratory} % Organization
    {Corvallis, OR} % Location
    {2018 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item{Utilize configuration management software to deploy and maintain infrastructure including servers, workstations, and network equipment.}
         \item{Write unit and integration tests for all server configurations.}
         \item{Work with the Open Source community, other hosted partners and developers at the OSL to determine needs.}
         \item{Work with fellow students to review existing and new code for readability, quality, and correctness.}
         \item{Develop skills in support of primary job functions. Research new tools and methods.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Infrastructure Engineer} % Job title
    {Tag1} % Organization
    {Remote} % Location
    {2019 - 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item{Utilize configuration management software to deploy and maintain infrastructure, and implement integration testing, supporting applications such as Drupal sites, APIs, and Solr clusters,.}
         \item{Work with various clients to develop and maintain new and existing infrastructure.}
         \item{Utilized infrastructure technologies such as Ansible, Pulumi, Kubernetes/Kustomize, Helm, Terraform, etc.}
         \item{Deployed and/or migrated applications to various infrastructures. e.g. AWS, Acquia, or client provided infrastructure.}
         \item{Created, maintained, and implemented CI/CD testing and deployment frameworks such as Github workflows, ArgoCD, and proprietary client software.}
         \item{Contributed to Tag1's open source partner project with Google, 'Gander'. Rapidly built and deployed the public instance of the app to AWS in two week time frame so that it could be showcased at Drupalcon. Gander is a preconfigured Open Telemetry stack relying on Prometheus, Grafana, and Grafana Tempo used for performance monitoring on Drupal core.}
      \end{cvitems}
    }

\end{cventries}
